Multi-level modeling with Openflexo/\FML

### 2021-09-27 4-technology.tex

  // Abstract concept BPMNElement defining
  // a name
  abstract concept BPMNElement {
    String name;
  }

@@

    // Describe here properties and
    // behaviours for BPMNProcess concept
    ...

@@

        // Describe here properties and
        // behaviours for BPMNTask concept
        ...

@@

\noteSylvain{Faut-il montrer des exemples de comportement aussi ?}

>>>>

  // Abstract concept BPMNElement defining
  // a name
  abstract concept BPMNElement {
    String name;
    // A basic constructor
    create(String name) {
      this.name = name;
    }
  }

@@

    // A basic constructor
    create(String name) {
      super(name);
    }
    // Describe here other properties and
    // behaviours for BPMNProcess concept
    ...

@@

      // A basic constructor
      create(String name) {
        super(name);
      }
      // Encodes execution of task
      execute() {
        log("Execute task "+name);
        ...
      }
      // Describe here other properties and
      // behaviours for BPMNTask concept
      ...

@@
